HUME: Human UCCA-Based Evaluation of Machine Translation

### 2016-06-02 paper/main.tex
minor

We proceed to detailing how judgements on the semantic units
of the source are aggregated into a composite score. 
%While future extensive empirical evaluation with HUME and its application to MT
%system tuning may suggest more complex definition,
%as a starting point we take a parsimonious approach,
We start by taking a very simple approach and compute an accuracy score.
Let $\Green(s,t)$, $\Adequate(s,t)$ and $\Orange(s,t)$ be the number of Green, Adequate and Orange
units respectively. Let $\Units(s)$ be the number of units marked with any of the labels.
Then HUME's composite score is:

@@

\com{
In Figure~\ref{mttool} you we show the MT evaluation tool. The sentence at the top shows the complete MT system output. Underneath the MT output is the  source sentence.  Underneath the source sentence we see its expandable semantic tree structure with both lexical and structural nodes. atomic nodes only have traffic light annotation, whereas a structural node would normally be labelled ``A'' or ``B'' but could also be labelled as a lexical node, in the case where there is no word to word correspondence for the translation of its children.

>>>>

We proceed to detailing how judgements on the semantic units
of the source are aggregated into a composite score. 
%While future extensive empirical evaluation with HUME and its application to MT
%system tuning may suggest more complex definition,
%as a starting point we take a parsimonious approach,
We start by taking a very simple approach and compute an accuracy score.
Let $\Green(s,t)$, $\Adequate(s,t)$ and $\Orange(s,t)$ be the number of Green, Adequate and Orange
units, respectively. Let $\Units(s)$ be the number of units marked with any of the labels.
Then HUME's composite score is:

@@

\com{
In Figure~\ref{mttool}, we show the MT evaluation tool. The sentence at the top shows the complete MT system output. Underneath the MT output is the  source sentence.  Underneath the source sentence we see its expandable semantic tree structure with both lexical and structural nodes. atomic nodes only have traffic light annotation, whereas a structural node would normally be labelled ``A'' or ``B'' but could also be labelled as a lexical node, in the case where there is no word to word correspondence for the translation of its children.
